---
title: 'AinB Assignment: Group 10'
author: Joaquin Coitino, Wing Yung Ho, Andrea Iglesias Villegas, Jason Kuilan, Lukas
  Wolff, Dian Yue Josef Zhu
date: "12/14/2016"
output:
  html_document:
    code_folding: hide
    number_sections: yes
    theme: readable
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
  word_document:
    toc: yes
header-includes: \usepackage{float}
---

<br>
<br>
<p style="border:1.5px; border-style:solid; border-color:#000000; padding: 1em;">This report contains interactive elements and has the best user experience if a web browser is used. Printing is possible. However, will not result in an optimal reading experience. The `R` code used to perform these analyses has been provided as supplementary files, and can be viewed in this report using the _Code_ buttons to toggle code viewing. All files are available online on Github [here](https://github.com/Josef123456/Analytics_for_Business_Group10.git).</p>

```{r, echo=FALSE, message=FALSE}
library(AER)
library(pscl)
library(MASS)
library(stargazer)
library(igraph)
library(pander)
library(knitr)
library(dplyr)
library(broom)
```

#Introduction

Before Group 10 began working on the project, the data was cleaned since some students were voting themselves.

```{r, include=FALSE}
setwd("/Users/Josef/Desktop/Analytics_for_Business_Group10/")
knitr::opts_chunk$set(echo = TRUE)
```


```{r echo=FALSE}
people <- read.csv("../Analytics_for_Business_Group10/Question1/peoplepickinganonymised.csv", header=TRUE)
friendship <- subset(people, select = -c(1:3,64:length(people)))
advice <- subset(people, select = -c(1:63, 124:length(people)))
creat <- subset(people, select = -c(1:123, 184:length(people)))
implem <-subset(people, select = -c(1:183, 244:length(people)))
infl <-subset(people, select = -c(1:243, 304:364))
```

```{r echo=FALSE}
colnames(friendship) <- seq(1,60,by=1)
colnames(creat) <- seq(1,60,by=1)
colnames(implem) <- seq(1,60,by=1)
colnames(infl) <- seq(1,60,by=1)
```

```{r echo=FALSE, message=FALSE, include=FALSE}
friendship[row(friendship) == col(friendship)] <- 0
creat[row(creat) == col(creat)] <- 0
implem[row(implem) == col(implem)] <- 0
infl[row(infl) == col(infl)] <- 0
```


```{r}
#write.csv(friendship, "friendshipmat.csv")
#write.csv(creat, "creatmat.csv")
#write.csv(implem, "implemmat.csv")
#write.csv(infl, "inflmat.csv")
```

#Regressions

As a starting point, you might like to know how popularity is related to being picked in the other three networks. To assess this, use in-degrees centrality in the Royal Albert hall network as an independent variable in three regressions, one for each of the other teams / networks, where the dependent variable in those regressions will also be in-degrees centrality in those networks. As to estimation, examine the data and select the right estimation method for (e.g., OLS vs. Poisson or negative binomial). Explain your choice of model, submit tables showing your results, and briefly explain what you found. Note: for this task, you are not required to assemble a proper set of controls to rule out alternative explanations; we are only exploring relationships among variables.

__Answer:__

To regress the influence of friendship over individuals’ choices, we must decide between running negative binomial and Poisson models, which are both applicable to count data but the former is not affected by overdispersion.

```{r}
graduation <- read.csv('../Analytics_for_Business_Group10/Question1/peoplepickinganonymisedwoselfvotes.csv', header = TRUE)
centrality <- data.frame(id = graduation$id, friendcent = NA)
friendcols <- c( which(colnames(graduation)=='friend_01'):which(colnames(graduation)=='friend_60'))
advicecols <- c( which(colnames(graduation)=='advice_01'):which(colnames(graduation)=='advice_60'))
creatcols <- c( which(colnames(graduation)=='creat_01'):which(colnames(graduation)=='creat_60'))
inflcols <- c( which(colnames(graduation)=='infl_01'):which(colnames(graduation)=='infl_60'))
implcols <- c( which(colnames(graduation)=='impl_01'):which(colnames(graduation)=='impl_60'))

centrality <- data.frame(id = graduation$id)
centrality$friendship <- colSums(graduation[friendcols])
centrality$advice <- colSums(graduation[advicecols])
centrality$creativity <- colSums(graduation[creatcols])
centrality$influence <- colSums(graduation[inflcols])
centrality$implementation <- colSums(graduation[implcols])
```

<br />
In order to make this decision, we test for overdispersion (odTest):

```{r}
creat.model <- glm.nb(creativity ~ friendship, data = centrality)
infl.model <- glm.nb(influence ~ friendship, data = centrality)
impl.model <- glm.nb(implementation ~ friendship, data = centrality)

#odTest_creat <- odTest(creat.model)
#odTest_infl <- odTest(infl.model)
#odTest_impl <- odTest(impl.model)
```
```{r, include=FALSE}
odTest_creat <- odTest(creat.model)
odTest_infl <- odTest(infl.model)
odTest_impl <- odTest(impl.model)
```
<br />
*Likelihood ratio test of $H_0$: the restriction of mean = variance in the Poisson model is true*

||Creativity Model|Influence Model|Implementation Model|
|:------:|:------:|:------:|:------:|
|P-value|0.004049|2.948 x 10^14|0.0006068|

In all the cases, the test provides evidence of the presence of overdispersion at a 95% significance level, which allows us to prefer the negative binomial models:
<br />
<br />

```{r, results='asis', echo = TRUE, fig.align="center"}
stargazer(creat.model, infl.model, impl.model, header = FALSE, table.placement = "H", type = "html", notes.align = "l")
```

<br />
<br />
All in all, the relationship between the friendship factor and the indegree counts is both positive and statistically significant for all three categories.


***

#Cosine Similarity
Your leaders should show smart flexibility in picking different people for different tasks. To assess this for each team, treat each person’s picks and non-picks for every person in the class as a binary vector for that team, and use cosine similarity to develop a score that represents individual flexibility of picks across the four networks. Explain the score, and provide a table that ranks all IDs by your score; include the ID, the actual score, and a Z-score for your flexibility score

__Answer:__

The cosine similarity was calculated to evaluate the flexibility of potential leaders. The method compares the vector of the friendship choices with the vectors for creativity, influence and implementation. This represents whether someone only picked his friends in all categories or adjusted regarding the task. A high score indicates low flexibility and might be an indicator for missing leadership skills.

<br />

```{r}
cosine <- read.csv('../Analytics_for_Business_Group10/Question2/GroupProjectCosineSimilarityExcelTable.csv', header = TRUE)

cosine_Table<- data.frame(cosine$id, round(cosine$Score,6), cosine$Z_score)

DT::datatable(cosine_Table,
              colnames = c("ID", "Score", "Z-Score"),
              caption = "Flexibility Table")
```


***

#Leaders 
Using the flexibility analysis in problem 1 and any other criteria you want to introduce, pick the three IDs (individuals) you want to have as leaders for the three teams. Again, explain the logic of your scoring, any qualitative considerations you deem important, and of course, your selections.

__Answer:__

__Page Rank__:

After evaluating the pagerank for creativity, influence, and implementation and writing them out as Spreadsheets, we used these to facilitate three Spreadsheets containing:

  + average cosine similarity
  
  + pagerank for respective category
  
  + average pagerank for the successors
  
  + friendship indegree

__Outcome:__

To pick our leaders we decided to use PageRank to evaluate the task specific ability of a person supported by our flexibility score from task 2 to indicate leadership potential. Additionally we considered the friendship in degree if it was extremely high, as it might constrain the decisions for the group members, although we put the focus on the PageRank score. Moreover, the creativity leader selected was required to have chosen a big party in the survey.

Our final picks for the leaders are:

  + Creativity: 7
  + Influence: 21
  + Implementation: 19


## Creativity, Influence, Implementation Table {.tabset}

### Creativity Table

```{r, fig.align='centre', eval = T}
creattable <- read.csv("../Analytics_for_Business_Group10/Question3/Creativity Table.csv")
creat_table <- data.frame(creattable$id, round(creattable$Creativity.Page.Rank,6), round(creattable$Cosine.similarity,6), round(creattable$Overall.Average.Page.Rank.of.Successors,6), round(creattable$Average.Creativity.Page.Rank.Successors,6), round(creattable$Frienship.indegree,6))


DT::datatable(creat_table,
              colnames = c("ID", "Creativity Page Rank", "Cosine similarity",
                           "Overall Average Page Rank of Successors",
                           "Average Creativity Page Rank Successors", "Frienship indegree"),
              caption = "Creativity Table")
```

### Influence table
```{r , fig.align = 'centre', eval = T}
infltable <- read.csv("../Analytics_for_Business_Group10/Question3/Influence Table.csv")
infl_table <- data.frame(infltable$id, round(infltable$Influence.Page.Rank,6), round(infltable$Cosine.similarity,6), round(infltable$Overall.Average.Page.Rank.of.Successors,6), round(infltable$Average.Influence.Page.Rank.Successors,6), round(infltable$Frienship.indegree,6))


DT::datatable(infl_table,
              colnames = c("ID", "Influence Page Rank", "Cosine similarity",
                           "Overall Average Page Rank of Successors",
                           "Average Influence Page Rank Successors", "Frienship indegree"),
              caption = "Influence Table")
```

### Implementation table
```{r network_bet, fig.align = 'centre', eval = T}
impltable <- read.csv("../Analytics_for_Business_Group10/Question3/Implementation Table.csv")
impl_table <- data.frame(impltable$id, round(impltable$Implementation.Page.Rank,6), round(impltable$Cosine.similarity,6), round(impltable$Overall.Average.Page.Rank.of.Successors,6), round(impltable$Average.Implementation.Page.Rank.Successors,6), round(impltable$Frienship.indegree,6))


DT::datatable(impl_table,
              colnames = c("ID", "Impl Page Rank", "Cosine similarity",
                           "Overall Average Page Rank of Successors",
                           "Average Impl Page Rank Successors", "Frienship indegree"),
              caption = "Implementation Table")
```


## Approach:

_Below we provided our code to justify our PageRank calulations:_

Here is the code snippet for friendship:
```{r friendship}
friendship <- graduation[,c( which(colnames(graduation)=='friend_01'):which(colnames(graduation)=='friend_60'))]
mat_friendship <- data.matrix(friendship, rownames.force = NA)

friendship.g <- graph.adjacency(mat_friendship, mode = "directed", weighted = NULL, diag = TRUE, add.colnames = NULL, add.rownames = NA) 

## Ranking advice by a page rank
page.ranking.friendship <- page.rank(friendship.g, vids=V(friendship.g))

## Sorting the page rank on highest value based on id with top 3 
sort.friendship <- sort.list(page.ranking.friendship$vector, decreasing = TRUE)
top3.friendship <- sort.friendship[1:10]
sorted.f <- page.ranking.friendship$vector[top3.friendship]

#pander(sorted.f,digits = 2)
```

Here is the code snippet for advice:
```{r advice}
advice <- graduation[,c( which(colnames(graduation)=='advice_01'):which(colnames(graduation)=='advice_60'))]
mat_advice <- data.matrix(advice, rownames.force = NA)

advice.g <- graph.adjacency(mat_advice, mode = "directed", weighted = NULL, diag = TRUE, add.colnames = NULL, add.rownames = NA) 

## Ranking advice by a page rank
page.ranking.advice <- page.rank(advice.g, vids=V(advice.g))

## Sorting the page rank on highest value based on id with top 3
sort.advice <- sort.list(page.ranking.advice$vector, decreasing = TRUE)
top3.advice <- sort.advice[1:10]
sorted.a <- page.ranking.advice$vector[top3.advice]

#pander(sorted.a,digits = 2)
```

Here is the code snippet for creativity:
```{r Creativity}
creat <- graduation[,c( which(colnames(graduation)=='creat_01'):which(colnames(graduation)=='creat_60'))]
mat_creat <- data.matrix(creat, rownames.force = NA)

creat.g <- graph.adjacency(mat_creat, mode = "directed", weighted = NULL, diag = TRUE, add.colnames = NULL, add.rownames = NA) 
## Ranking advice by a page rank
page.ranking.creat <- page.rank(creat.g, vids=V(creat.g))
creat.ranked <- lapply(page.ranking.creat, function(x) x[which.max(x)])

#write.csv(page.ranking.creat$vector, file = "CreativityPageRank.csv")

## Sorting the page rank on highest value based on id
sort.creat <- sort.list(page.ranking.creat$vector, decreasing = TRUE)
top3.creat <- sort.creat[1:10]
sorted.c <- page.ranking.creat$vector[top3.creat]

#pander(sorted.c,digits = 2)
```

Here is the code snippet for influence:
```{r Influence}
infl <- graduation[,c( which(colnames(graduation)=='infl_01'):which(colnames(graduation)=='infl_60'))]
mat_infl <- data.matrix(infl, rownames.force = NA)

infl.g <- graph.adjacency(mat_infl, mode = "directed", weighted = NULL, diag = TRUE, add.colnames = NULL, add.rownames = NA) 

## Ranking infl by a page rank
page.ranking.infl <- page.rank(infl.g, vids=V(infl.g))
infl.ranked <- lapply(page.ranking.infl, function(x) x[which.max(x)])

#write.csv(page.ranking.infl$vector, file = "InfluencePageRank.csv")

## Sorting the page rank on highest value based on id
sort.infl <- sort.list(page.ranking.infl$vector, decreasing = TRUE)
top3.infl <- sort.infl[1:10]
sorted.in <- page.ranking.infl$vector[top3.infl]

#pander(sorted.in,digits = 2)
```

Here is the code snippet for implementation:
```{r Implementation}
impl <- graduation[,c( which(colnames(graduation)=='impl_01'):which(colnames(graduation)=='impl_60'))]
mat_impl <- data.matrix(impl, rownames.force = NA)

impl.g <- graph.adjacency(mat_impl, mode = "directed", weighted = NULL, diag = TRUE, add.colnames = NULL, add.rownames = NA) 

## Ranking impl by a page rank
page.ranking.impl <- page.rank(impl.g, vids=V(impl.g))
impl.ranked <- lapply(page.ranking.impl, function(x) x[which.max(x)])

#write.csv(page.ranking.impl$vector, file = "ImplementationPageRank.csv")

## Sorting the page rank on highest value based on id
sort.impl <- sort.list(page.ranking.impl$vector, decreasing = TRUE)
top3.impl <- sort.impl[1:10]
sorted.impl <- page.ranking.impl$vector[top3.impl]

#pander(sorted.impl,digits = 2)
```

<br />
<br />
_The table below contains the 10 persons with the highest PageRank score for every task category plus friendship._

```{r, echo=FALSE}
top10_id <- c(1:10)
allRanked <- data_frame(top10_id,top3.friendship, top3.creat, top3.infl, top3.impl) 
allRanked %>% kable(caption = "Top Ten: Page Rank Summary", col.names = c("Ranking","Friendship", "Creativity", "Influence", "Implementation"))
```

The python code can be found [here](http://pastebin.com/TygYBfkX) and is also available in the appendix section.

***

#ID Rankings
<p><i>Finally, produce three tables that rank IDs by a networkspecific constructed measure of value, which is some kind of cost-benefit ratio. Explain the logic of your measure. To get you started, recall that the “cost” of each pick is the in-degrees score in the Royal Albert Hall network, so that is your denominator.</i></p>


__Answer:__

We chose PageRank as a network measure to evaluate the ability of a person for a specific task. Hence our cost-benefit ratio is  the PageRank score for the respective category divided by the friendship in-degree of the person. Finally we created three tables with the IDs, PageRank score, friendship in-degree and our cost-benefit ratio.


## Cost-Benefit Ratio {.tabset}

### Creativity

```{r, fig.align='centre', eval = T}
creattable <- read.csv("../Analytics_for_Business_Group10/Question4/Creativity Table.csv")
creat_table <- data.frame(creattable$id, round(creattable$Creativity.Page.Rank,6), round(creattable$Frienship.indegree,6), round(creattable$Creativity.Ratio,6))


DT::datatable(creat_table,
              colnames = c("ID", "Creativity Page Rank","Frienship indegree","Creativity: Cost-Benefit Ratio"),
              caption = "Creativity: Cost-Benefit Ratio")
```

### Influence

```{r, fig.align = 'centre', eval = T}
infltable <- read.csv("../Analytics_for_Business_Group10/Question4/Influence Table.csv")
infl_table <- data.frame(infltable$id, round(infltable$Influence.Page.Rank,6), round(infltable$Frienship.indegree,6), round(infltable$Influence.Ratio,6))


DT::datatable(infl_table,
              colnames = c("ID", "Influence Page Rank","Frienship indegree","Influence: Cost-Benefit Ratio"),
              caption = "Influence: Cost-Benefit Ratio")
```

### Implementation
```{r, fig.align = 'centre', eval = T}
impltable <- read.csv("../Analytics_for_Business_Group10/Question4/Implementation Table.csv")
impl_table <- data.frame(impltable$id, round(impltable$Implementation.Page.Rank,6), round(impltable$Frienship.indegree,6), round(impltable$Implementation.Ratio,6))


DT::datatable(impl_table,
              colnames = c("ID", "Impl Page Rank", "Frienship indegree","Impl.: Cost-Benefit Ratio"),
              caption = "Implementation: Cost-Benefit Ratio")
```

***

#Conclusion

```{r  include=FALSE}
library(igraph)
library(sp)
set.seed(3)
friendship <- read.csv("../Analytics_for_Business_Group10/Question1/Cleaned Spreadsheet/friendshipmat.csv", header=TRUE)
friendship <- subset(friendship, select = -c(X))
rownames(friendship) <- seq(1:60)
colnames(friendship) <- seq(1:60)
```


```{r, include=FALSE}
friendship <- data.matrix(friendship)
g <- graph.adjacency(friendship, mode=c("directed"))
```

After running the optimization model in __Ampl__ to yield the best groups for our chosen leaders, the social dynamics of the cohort, which cannot be captured in the model, are explored. Therefore, a community detection algorithms was used to find a ‘best partition’ for the overall collective in order to visualize the leaders’ position in the friendship network of the class. In the graph below, the class is divided into 4 communities (The Ampl code can be found on [Github](https://github.com/Josef123456/Analytics_for_Business_Group10.git) and in the appendix section):

```{r echo=FALSE, fig.width=14, fig.height = 6, fig.align='center'}
#Sample community graph (R)
communities <- cluster_infomap(g)
plot( g, layout=layout.fruchterman.reingold, vertex.size=15, vertex.color = membership(communities), vertex.label.dist=0.1, edge.arrow.size=0.3)
```

##Evaluation 

###Option 1
```{r echo=FALSE, fig.height = 5.8, fig.align='center'}
V(g)$color <- "snow2"
V(g)[7]$color <- "steelblue3"
V(g)[c(24,35,49,50)]$color <- "skyblue1"
V(g)[19]$color <- "firebrick3"
V(g)[c(1,8,30,33)]$color <- "indianred1"
V(g)[21]$color <- "seagreen3"
V(g)[c(20,22,34,38)]$color <- "darkseagreen1"
plot(g, layout=layout.lgl, vertex.size=15,
     vertex.label.dist=0.1, edge.arrow.size=0.05)
legend("topleft", inset = 0, 
        cex = 0.8, 
        legend = c("Implementation", "Influence", "Creativity"), 
        text.col = c("red", "lightgreen","lightblue"),
        col = c("red", "green","blue"), 
        title = "Categories", 
        horiz=FALSE,
        text.font=3, 
        pch = c(16,16))
```

###Option 2
```{r echo=FALSE, fig.align='center', fig.height = 6}
V(g)$color <- "snow2"
V(g)[21]$color <- "steelblue3"
V(g)[c(7,24,35,49)]$color <- "skyblue1"
V(g)[33]$color <- "firebrick3"
V(g)[c(8,1,30,22)]$color <- "indianred1"
V(g)[19]$color <- "seagreen3"
V(g)[c(20,52,34,38)]$color <- "darkseagreen1"
plot(g, layout=layout.lgl, vertex.size=15,
     vertex.label.dist=0.1, edge.arrow.size=0.05)
legend("topleft", inset = 0, 
        cex = 0.8, 
        legend = c("Implementation", "Influence", "Creativity"), 
        text.col = c("red", "lightgreen","lightblue"),
        col = c("red", "green","blue"), 
        title = "Categories", 
        horiz=FALSE,
        text.font=3, 
        pch = c(16,16))
```


According to the graphs, only one of the team members for all categories comes from a different community than the rest. In the case of the implementation team, this ensures the members have a close enough relationship to effectively work together. However, for the creativity and influence teams, members should preferably be distributed across the network to better represent everyone’s interests. Consequently, a constraint is added to the model which allows no more than two members of the team for influence and creativity to belong to the same community. The new model that results for the creativity team has an overall pagerank significantly lower. However, the difference for the influence one is not considerably large. Therefore, for the former team the previous option is chosen but for the latter team the new one is preferred.

###Final Option
And below, the plot depicts the result of our final decision for the groups:

```{r echo=FALSE, fig.height = 5.8, fig.align='center'}
V(g)$color <- "snow2"
V(g)[7]$color <- "dodgerblue3"
V(g)[c(24,35,49,50)]$color <- "skyblue1"
V(g)[19]$color <- "brown2"
V(g)[c(1,8,30,33)]$color <- "salmon"
V(g)[21]$color <- "seagreen3"
V(g)[c(25,34,56,23)]$color <- "darkseagreen1"
plot(g, layout=layout.fruchterman.reingold, vertex.size=15, vertex.color=V(g)$color,
     vertex.label.dist=0.1, edge.arrow.size=0.05, vertex.label.color = "grey26")
legend("topleft", inset = 0, 
        cex = 0.8, 
        legend = c("Implementation", "Influence", "Creativity"), 
        text.col = c("red", "lightgreen","lightblue"),
        col = c("red", "green","blue"), 
        title = "Categories", 
        horiz=FALSE,
        text.font=3, 
        pch = c(16,16))
``` 

***

#Bonus 

<p><i>Revisiting question 2, cosine similarity is but one method of assessing flexibility. If you allow yourself to think beyond using that technique to compare the similarity of two vectors of picks (0s and 1s), what other more creative method might you devise? How does it compare to cosine similarity? If it is different, can you provide a qualitative description of what your measure captures that is not in cosine similarity? Is it better?</i></p>

__Answer:__

Before we can decide if another method would be better suited we must first explore what cosine similarity (CS) is, what it tells us, and why this is important. CS takes the angle between two vectors and returns a value between 0 and 1 depending on the angle between the two vectors. Vectors with a small angle between them will give us a value close to 1, while vectors with a large angle will give values close to 0. Someone who has low CS shows they choose different people than their friend circle, likewise, someone with a high CS made their choices like their friend circle. While most people are comfortable working within their friend group, some see the benefit of working outside their circle to get different outlooks on various situations. 
	
While CS is good measure of someone’s adaptability, we do not agree that it is the best in our case. After exploring other options, we think Jaccard similarity (JS) would be the appropriate method to use. JS divides the intersection of a set by the union of the same set. This method accounts for both the magnitude and angle between vectors. The values of JS are like the CS method, with values ranging between 0 (for differing vectors) and 1 (for similar vectors). 

As in our case not all people have the same number of choices, we think the magnitude of the vector should be integrated as well into our calculations.

#Appendix:

### Question 3: Leaders 

```
import numpy as np
import pandas as pd
import networkx as nx
import pylab as pl


friends = pd.read_csv("/Users/joaquincoitino/Desktop/peoplepickinganonymisedwoselfvotes.csv", header=0, index_col=0)

cosine_similarity = pd.read_csv("/Users/joaquincoitino/Desktop/GroupProjectCosineSimilarityExcelTable.csv", header=0, index_col=0)

       
def mean(numbers):
   return float(sum(numbers)) / max(len(numbers), 1)     


### Average PageRank for Creativity:

creat_pagerank = pd.read_csv("/Users/joaquincoitino/Desktop/CreativityPageRank.csv", usecols = ['x'])

creat_adj_matrix = friends.loc[:,'creat_01':'creat_60'].as_matrix()

creat_graph = nx.from_numpy_matrix(creat_adj_matrix, create_using = nx.DiGraph())

creat_pr_successors = []

for i in creat_graph.nodes_iter():
    list_pr =[]

    for j in creat_graph.successors(i):
        list_pr.append(creat_pagerank.loc[j,'x'])
    creat_pr_successors.append(mean(list_pr))
    
   
### Average PageRank for Influence:
    
infl_pagerank = pd.read_csv("/Users/joaquincoitino/Desktop/InfluencePageRank.csv", usecols = ['x'])

infl_adj_matrix = friends.loc[:,'infl_01':'infl_60'].as_matrix()

infl_graph = nx.from_numpy_matrix(infl_adj_matrix, create_using = nx.DiGraph())

infl_pr_successors = []

for i in infl_graph.nodes_iter():
    list_pr =[]

    for j in infl_graph.successors(i):
        list_pr.append(infl_pagerank.loc[j,'x'])
    infl_pr_successors.append(mean(list_pr))


### Average PageRank for Implementation:
    
impl_pagerank = pd.read_csv("/Users/joaquincoitino/Desktop/ImplementationPageRank.csv", usecols = ['x'])

impl_adj_matrix = friends.loc[:,'impl_01':'impl_60'].as_matrix()

impl_graph = nx.from_numpy_matrix(impl_adj_matrix, create_using = nx.DiGraph())

impl_pr_successors = []

for i in impl_graph.nodes_iter():
    list_pr =[]

    for j in impl_graph.successors(i):
        list_pr.append(impl_pagerank.loc[j,'x'])
    impl_pr_successors.append(mean(list_pr)) 

    
### Average pagerank for all categories

avg_pagerank_succe = [(x+y+z)/3 for x,y,z in zip(creat_pr_successors, infl_pr_successors, impl_pr_successors)]
    
### Frienship indegree

friend_adj_matrix = friends.loc[:,'friend_01':'friend_60'].as_matrix()

friend_graph = nx.from_numpy_matrix(friend_adj_matrix, create_using = nx.DiGraph())

friend_indegree = friend_graph.in_degree()

list_f_indegree = []

for i in friend_indegree:
    list_f_indegree.append(friend_indegree[i])

## pagerank/degree ratio

ratio_pr_findegree_creat = [x/y for x, y in zip(creat_pagerank.loc[:,'x'], list_f_indegree)]
ratio_pr_findegree_infl = [x/y for x, y in zip(infl_pagerank.loc[:,'x'], list_f_indegree)]
ratio_pr_findegree_impl = [x/y for x, y in zip(impl_pagerank.loc[:,'x'], list_f_indegree)]
                           
cosine = cosine_similarity.loc[:,'Score'].tolist()

pr_creat = creat_pagerank.loc[:,'x'].tolist()
pr_infl = infl_pagerank.loc[:,'x'].tolist()
pr_impl = impl_pagerank.loc[:,'x'].tolist()
                           
creat_dataframe = pd.DataFrame.from_items([('id', list(range(1,61))), ('Creativity Page Rank', pr_creat), ('Cosine similarity', cosine), ('Overall Average Page Rank of Successors', avg_pagerank_succe), ('Average Creativity Page Rank Successors', creat_pr_successors), ('Frienship indegree', list_f_indegree), ('Creativity Ratio', ratio_pr_findegree_creat)])
creat_dataframe.to_csv('Creativity Table.csv', index = False)

infl_dataframe = pd.DataFrame.from_items([('id', list(range(1,61))), ('Influence Page Rank', pr_infl), ('Cosine similarity', cosine), ('Overall Average Page Rank of Successors', avg_pagerank_succe), ('Average Influence Page Rank Successors', infl_pr_successors), ('Frienship indegree', list_f_indegree), ('Influence Ratio', ratio_pr_findegree_infl)])
infl_dataframe.to_csv('Influence Table.csv', index = False)

impl_dataframe = pd.DataFrame.from_items([('id', list(range(1,61))), ('Implementation Page Rank', pr_impl), ('Cosine similarity', cosine), ('Overall Average Page Rank of Successors', avg_pagerank_succe), ('Average Implementation Page Rank Successors', impl_pr_successors), ('Frienship indegree', list_f_indegree), ('Implementation Ratio', ratio_pr_findegree_impl)])
impl_dataframe.to_csv('Implementation Table.csv', index = False)
```

### Optimization Model AMPL

__maxpagerank.mod:__
```
set id ordered ;
param create_pr {id};
param imp_pr {id};
param inf_pr {id};
param friendship_indegree {id};

data allpagerank.dat;
param N := 3;

var x {i in id , 1.. N} binary;

maximize pr: sum {i in id} (x[i,1]*create_pr[i]+ x[i,2]*inf_pr[i] +x[i,3]*imp_pr[i]);

subject to create_friendship: sum {i in id}  (x[i,1]*friendship_indegree[i]) <= 30;
subject to inf_friendship: sum {i in id}  (x[i,2]*friendship_indegree[i]) <= 30;
subject to imp_friendship: sum {i in id}  (x[i,3]*friendship_indegree[i]) <= 30;
subject to create_4members:  sum {i in id} (x[i,1]) = 5;
subject to inf_4members:  sum {i in id} (x[i,2]) = 5;
subject to imp_4members:  sum {i in id} (x[i,3]) = 5;
subject to picked_once {i in id}: x[i,1] + x[i,2] + x[i,3] <= 1;
subject to create_leader: x[7,1] = 1;
subject to inf_leader: x[21,2] = 1;
subject to imp_leader: x[19,3] = 1;
```

__maxpagerank_withcomm.mod__ (With community):
```
set id ordered ;
param create_pr {id};
param imp_pr {id};
param inf_pr {id};
param friendship_indegree {id};

data allpagerank.dat;
param N := 3;

var x {i in id , 1.. N} binary;

maximize pr: sum {i in id} (x[i,1]*create_pr[i]+ x[i,2]*inf_pr[i] +x[i,3]*imp_pr[i]);

subject to create_friendship: sum {i in id}  (x[i,1]*friendship_indegree[i]) <= 30;
subject to inf_friendship: sum {i in id}  (x[i,2]*friendship_indegree[i]) <= 30;
subject to imp_friendship: sum {i in id}  (x[i,3]*friendship_indegree[i]) <= 30;
subject to create_4members:  sum {i in id} (x[i,1]) = 5;
subject to inf_4members:  sum {i in id} (x[i,2]) = 5;
subject to imp_4members:  sum {i in id} (x[i,3]) = 5;
subject to picked_once {i in id}: x[i,1] + x[i,2] + x[i,3] <= 1;
subject to create_leader: x[7,1] = 1;
subject to inf_leader: x[21,2] = 1;
subject to imp_leader: x[19,3] = 1;
subject to creat_community1: x[51,1]+ x[56,1]+x[28,1]+x[14,1]+ x[12,1] <=2;
subject to creat_community2: x[32,1]+ x[54,1]+x[43,1]+x[41,1]+ x[42,1]+x[55,1]+x[16,1]+x[18,1]+x[13,1] <=2;
subject to creat_community3: x[49,1]+ x[27,1]+x[23,1]+x[57,1]+ x[4,1]+x[5,1]+x[11,1]+x[2,1]+x[44,1]+x[26,1]+x[36,1]+x[9,1]+x[40,1]+x[53,1]<=2;
subject to creat_community4: x[15,1]+ x[1,1]+x[29,1]+x[3,1]+ x[37,1]+x[21,1]+x[20,1]+x[60,1]+x[47,1]+x[38,1]+x[52,1]+x[33,1]+x[46,1]+x[59,1] +x[24,1]+x[19,1]+x[17,1]+x[34,1]+x[22,1] +x[7,1]+x[50,1]+x[6,1]+x[45,1]+x[35,1] +x[10,1]+x[30,1]+x[8,1]+x[31,1]+x[58,1] + x[48,1] + x[39,1]<=2;
subject to inf_community1: x[51,2]+ x[56,2]+x[28,2]+x[14,2]+ x[12,2] <=2;
subject to inf_community2: x[32,2]+ x[54,2]+x[43,2]+x[41,2]+ x[42,2]+x[55,2]+x[16,2]+x[18,2]+x[13,2] <=2;
subject to inf_community3: x[49,2]+ x[27,2]+x[23,2]+x[57,2]+ x[4,2]+x[5,2]+x[11,2]+x[2,2]+x[44,2]+x[26,2]+x[36,2]+x[9,2]+x[40,2]+x[53,2]<=2;
subject to inf_community4: x[15,2]+ x[1,2]+x[29,2]+x[3,2]+ x[37,2]+x[21,2]+x[20,2]+x[60,2]+x[47,2]+x[38,2]+x[52,2]+x[33,2]+x[46,2]+x[59,2] +x[24,2]+x[19,2]+x[17,2]+x[34,2]+x[22,2] +x[7,2]+x[50,2]+x[6,2]+x[45,2]+x[35,2] +x[10,2]+x[30,2]+x[8,2]+x[31,2]+x[58,2] + x[48,2] + x[39,2]<=2;
```